### 2022-03-21 manuscript.tex
Update 01.introduction.md [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/1a493f8ef1b1d34f03b4e1ee4cfd6e289b300a73.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/1a493f8ef1b1d34f03b4e1ee4cfd6e289b300a73/checks
https://github.com/scherzerthesis/thesis/actions/runs/2017749345

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/419ff731062cbb3fe3b1423f6c6a6cec111ea028/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/419ff731062cbb3fe3b1423f6c6a6cec111ea028}{scherzerthesis/thesis@419ff73}
on March 21, 2022.

@@

Often times, P53 is mutated in the DNA-binding domain at sites commonly referred to as "hotspots" due to there extraordinary frequency. These hotspot mutations poison the ability of p53 to bind DNA therefore blocking its function. Interestingly, since one mutated P53 can disrupt the entire P53 tetramer complex, a single mutation can exert dominant-negative effects by inhibiting the normal tumor suppressive functions of P53. Although one mutant P53 allele is enough to compromised transcriptional activity, there is still selective pressure to lose the other wild -type copy. Loss of hemizygosity implies there is still residual tumor suppression in the presence of a wild-type P53 allele.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/1a493f8ef1b1d34f03b4e1ee4cfd6e289b300a73/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/1a493f8ef1b1d34f03b4e1ee4cfd6e289b300a73}{scherzerthesis/thesis@1a493f8}
on March 21, 2022.

@@

Often times, P53 is mutated in the DNA-binding domain at sites commonly referred to as "hotspots" due to there extraordinary frequency. These hotspot mutations poison the ability of p53 to bind DNA therefore blocking its function. Interestingly, since one mutated P53 can disrupt the entire P53 tetramer complex, a single mutation can exert dominant-negative effects by inhibiting the normal tumor suppressive functions of P53. Although one mutant P53 allele is enough to compromised transcriptional activity, there is still selective pressure to lose the other wild -type copy. Loss of hemizygosity implies there is still residual tumor suppression in the presence of a wild-type P53 allele(Muzumdar \emph{et al.}, 2016).
